---
title       : Reproducible Pitch for a "Simple" Shiny App
subtitle    : Demonstrate the usefulness of Slidify as a means for a reproducible presentation. The very simplistic Shiny App is presented using Slidify, whereby the same interactive presentation can be reproduced many times very simply.
author      : John Michael Robertson
job         : In partial requirement for Coursera class - Developing Data Products by Johns Hopkins
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
```{r echo=FALSE}
library(markdown)
library(knitr)
```
## Reproducible Pitch

1. The "Simple Demo" Shiny App is a very simplistic demonstration of Shiny
2. Although basic and generic, the app illustrates the power of Shiny as a means for reproducible demonstrations
3. The "Simple Demo" Shiny App can be effecively used as a teaching illustration

### What type of app do you expect for demonstration purposes?
* Would you prefer something elaborate with lots of bells and whistles?
* Or, would a simple illustration be preferable?

--- .class #id 

## Overview of ShinyApp

The location of the "Simle Demo" Shiny App is :
[http://johnmichaelr.shinyapps.io/SimpleDemo](http://johnmichaelr.shinyapps.io/SimpleDemo)


<p>Purpose of the "Simple Demo" application is to illustrate the ease and simplicity of generating a Histogram with the "mtcars" dataset. The user can select any attribute from the mtcars dataset and a histogram will automatically display based upon the user attribute selection.</p>

### Example of output provided to user
``` {r echo=TRUE, fig.height=3, fig.width=7}
library(datasets)

hist(mtcars$mpg, xlab="mpg")

# close the plot
dev.off()
```

--- .class #id 

## Future Version of "Simple Demo"

<p>Future versions of the Simple Demo will include dynamic selection of a dataset from the "datasets" library. Another option is to include the linear model plot of the dynamically selected dataset and outcome~predictor.</p>

### Example of a future version
<p>Demonstrate the functionality of a plot with a linear model applied.</p>
``` {r echo=FALSE, fig.height=3, fig.width=7}
fit <- lm(mpg ~ wt, data=mtcars)
plot(x=mtcars$wt, y=mtcars$mpg, xlab="Weight", ylab="MPG")
abline(fit, col=2)

```


--- .class #id 

## Conclusion

<b>Keep It Simple</b>

* Simplicity keeps the focus on the tool
* User attention is drawn away when complexity is added

<p>
The "Simple Demo" is just what it says, very simple. A user or student can visualize the interactivity of Shiny without getting lost in too much complexity or visualizations. 
</p>

<em>The sole purpose of the app is to illustrate Shiny as:</em>

1. User Friendly Interactivity
2. Reproducible R code
3. Interactive R code
